---
title: "DCC-GARCH without S&P 500"
format: html
editor: visual
---

# DCC-GARCH Analysis without S&P 500

This file estimates a DCC-GARCH model for five Asian stock markets only: Shanghai Composite, Hang Seng, Nikkei 225, KOSPI and Singapore STI.

For direct comparability with the extended specification, both DCC-GARCH models use the same trading-date sample obtained by inner-joining the five Asian markets and the S&P 500. The S&P 500 determines the common dates but is not included as a variable in this baseline DCC-GARCH model.

The main purpose is to examine the dynamic conditional correlations between the Chinese stock market and other Asian markets.

## 1. Load Packages

```{r}
packages <- c(
  "readr", "dplyr", "lubridate", "rugarch", "rmgarch",
  "xts", "zoo", "ggplot2", "tidyr", "gt", "knitr"
)

# Load packages
lapply(packages, library, character.only = TRUE)
```

## 2. Import Daily Index Price Data

The repository includes a frozen local dataset ending on 2023-08-31. Rendering this document does not download or update market data.

```{r}
data_candidates <- c(
  "../../dataset/outputs/daily_prices_all_markets.csv",
  "dataset/outputs/daily_prices_all_markets.csv",
  "daily_prices_all_markets.csv"
)
data_path <- data_candidates[file.exists(data_candidates)][1]

if (is.na(data_path)) {
  stop("The frozen daily_prices_all_markets.csv included with the project was not found.")
}

daily_prices <- readr::read_csv(data_path)

head(daily_prices)
str(daily_prices)
```

## 3. Clean Date and Restrict Sample Period

```{r}
daily_prices <- daily_prices %>%
  mutate(Date = as.Date(Date)) %>%
  arrange(Date) %>%
  filter(
    Date >= as.Date("2003-01-01"),
    Date <= as.Date("2023-08-31")
  )

head(daily_prices)
tail(daily_prices)
summary(daily_prices)
colSums(is.na(daily_prices))
sum(duplicated(daily_prices$Date))
nrow(daily_prices)
```

## 4. Calculate Daily Log Returns

This step converts daily price indices into daily log returns. The S&P 500 is excluded in this version.

```{r}
daily_returns <- daily_prices %>%
  mutate(
    r_Shanghai = (log(Shanghai_Composite) - log(lag(Shanghai_Composite))) * 100,
    r_Hang_Seng = (log(Hang_Seng) - log(lag(Hang_Seng))) * 100,
    r_Nikkei_225 = (log(Nikkei_225) - log(lag(Nikkei_225))) * 100,
    r_KOSPI = (log(KOSPI) - log(lag(KOSPI))) * 100,
    r_STI = (log(STI) - log(lag(STI))) * 100
  ) %>%
  select(
    Date,
    r_Shanghai,
    r_Hang_Seng,
    r_Nikkei_225,
    r_KOSPI,
    r_STI
  ) %>%
  na.omit()

head(daily_returns)
tail(daily_returns)
summary(daily_returns)
colSums(is.na(daily_returns))
nrow(daily_returns)
```

## 4.1 Daily Data Audit and Descriptive Statistics

The audit table records how the common daily price sample becomes the return sample used in the DCC-GARCH estimation. The descriptive table is based on the five Asian return series included in the baseline model.

```{r}
daily_data_audit <- data.frame(
  Stage = c("Common six-market daily prices", "Baseline daily returns"),
  Observations = c(nrow(daily_prices), nrow(daily_returns)),
  Start_Date = c(as.character(min(daily_prices$Date)), as.character(min(daily_returns$Date))),
  End_Date = c(as.character(max(daily_prices$Date)), as.character(max(daily_returns$Date))),
  Missing_Values = c(sum(is.na(daily_prices)), sum(is.na(daily_returns))),
  Duplicate_Dates = c(sum(duplicated(daily_prices$Date)), sum(duplicated(daily_returns$Date)))
)

daily_data_audit

return_variables <- setdiff(names(daily_returns), "Date")

daily_descriptive_statistics <- do.call(rbind, lapply(return_variables, function(variable) {
  x <- daily_returns[[variable]]
  n <- length(x)
  x_mean <- mean(x)
  x_sd <- sd(x)
  skewness <- mean((x - x_mean)^3) / x_sd^3
  excess_kurtosis <- mean((x - x_mean)^4) / x_sd^4 - 3
  jb_statistic <- n / 6 * (skewness^2 + excess_kurtosis^2 / 4)

  data.frame(
    Variable = variable,
    N = n,
    Mean = x_mean,
    Std_Dev = x_sd,
    Minimum = min(x),
    Maximum = max(x),
    Skewness = skewness,
    Excess_Kurtosis = excess_kurtosis,
    JB_Statistic = jb_statistic,
    JB_p_value = pchisq(jb_statistic, df = 2, lower.tail = FALSE)
  )
}))

daily_descriptive_statistics
```

## 5. Export Cleaned Daily Returns

```{r}
write.csv(daily_returns, "daily_returns_for_dcc_no_sp500.csv", row.names = FALSE)
```

## 6. Prepare Data for DCC-GARCH

```{r}
# Keep only return variables for DCC-GARCH estimation
dcc_data_no_sp500 <- daily_returns %>%
  select(
    r_Shanghai,
    r_Hang_Seng,
    r_Nikkei_225,
    r_KOSPI,
    r_STI
  )

head(dcc_data_no_sp500)
summary(dcc_data_no_sp500)
```

## 7. Specify the DCC-GARCH Model

The model uses a univariate GARCH(1,1) specification for each market and then estimates a DCC-GARCH(1,1) model for the conditional correlations.

```{r}
# Univariate GARCH(1,1) specification for each market
uspec_no_sp500 <- ugarchspec(
  mean.model = list(armaOrder = c(0, 0), include.mean = TRUE),
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  distribution.model = "norm"
)

# Apply the same GARCH specification to all return series
multispec_model_no_sp500 <- multispec(replicate(ncol(dcc_data_no_sp500), uspec_no_sp500))

# DCC-GARCH(1,1) specification
dcc_spec_no_sp500 <- dccspec(
  uspec = multispec_model_no_sp500,
  dccOrder = c(1, 1),
  distribution = "mvnorm"
)
```

## 8. Estimate the DCC-GARCH Model

```{r}
dcc_fit_no_sp500 <- dccfit(
  dcc_spec_no_sp500,
  data = dcc_data_no_sp500
)

dcc_fit_no_sp500
```

## 9. Create DCC-GARCH Parameter Table

```{r}
dcc_param_table_no_sp500 <- as.data.frame(dcc_fit_no_sp500@mfit$matcoef)

dcc_param_table_no_sp500$Parameter <- rownames(dcc_param_table_no_sp500)

colnames(dcc_param_table_no_sp500) <- c(
  "Estimate",
  "Std_Error",
  "t_value",
  "p_value",
  "Parameter"
)

dcc_param_table_no_sp500 <- dcc_param_table_no_sp500 %>%
  select(Parameter, Estimate, Std_Error, t_value, p_value) %>%
  mutate(
    CI_Lower = Estimate - 1.96 * Std_Error,
    CI_Upper = Estimate + 1.96 * Std_Error
  )

dcc_param_gt_no_sp500 <- dcc_param_table_no_sp500 %>%
  gt() %>%
  tab_header(
    title = "DCC-GARCH Parameter Estimates",
    subtitle = "Five Asian stock markets, excluding S&P 500"
  ) %>%
  cols_label(
    Parameter = "Parameter",
    Estimate = "Estimate",
    Std_Error = "Std. Error",
    t_value = "t value",
    p_value = "p-value",
    CI_Lower = "95% CI Lower",
    CI_Upper = "95% CI Upper"
  ) %>%
  fmt_number(
    columns = c(Estimate, Std_Error, t_value, p_value, CI_Lower, CI_Upper),
    decimals = 6
  )

dcc_param_gt_no_sp500

gtsave(
  dcc_param_gt_no_sp500,
  filename = "dcc_garch_parameter_estimates_no_sp500.png"
)
```

## 10. Extract Dynamic Conditional Correlations

```{r}
# Extract dynamic correlation array
dcc_cor_no_sp500 <- rcor(dcc_fit_no_sp500)

# Check dimensions: market x market x time
dim(dcc_cor_no_sp500)
```

## 11. Average Dynamic Conditional Correlation Matrix

```{r}
avg_dcc_cor_matrix_no_sp500 <- apply(dcc_cor_no_sp500, c(1, 2), mean, na.rm = TRUE)

colnames(avg_dcc_cor_matrix_no_sp500) <- colnames(dcc_data_no_sp500)
rownames(avg_dcc_cor_matrix_no_sp500) <- colnames(dcc_data_no_sp500)

knitr::kable(
  avg_dcc_cor_matrix_no_sp500,
  digits = 4,
  caption = "Average Dynamic Conditional Correlation Matrix without S&P 500"
)
```

## 12. Pairwise Dynamic Correlation Table

This table reports the average dynamic conditional correlation for each market pair.

```{r}
make_corr_row <- function(x, pair_name) {
  x <- na.omit(x)
  coef <- mean(x)
  se <- sd(x) / sqrt(length(x))
  z_value <- coef / se
  p_value <- 2 * (1 - pnorm(abs(z_value)))
  ci_lower <- coef - 1.96 * se
  ci_upper <- coef + 1.96 * se
  
  data.frame(
    Pair = pair_name,
    Coef = coef,
    Std_Error = se,
    z = z_value,
    P_value = p_value,
    CI_Lower = ci_lower,
    CI_Upper = ci_upper
  )
}

market_names <- colnames(dcc_data_no_sp500)
pair_index <- combn(seq_along(market_names), 2)

pairwise_corr_table <- do.call(
  rbind,
  lapply(seq_len(ncol(pair_index)), function(i) {
    m1 <- pair_index[1, i]
    m2 <- pair_index[2, i]
    pair_name <- paste0("corr(", market_names[m1], ", ", market_names[m2], ")")
  make_corr_row(dcc_cor_no_sp500[m1, m2, ], pair_name)
  })
)

pairwise_corr_gt <- pairwise_corr_table %>%
  gt() %>%
  tab_header(
    title = "Pairwise Dynamic Conditional Correlations",
    subtitle = "DCC-GARCH estimated correlations without S&P 500"
  ) %>%
  cols_label(
    Pair = "Pair",
    Coef = "Coef.",
    Std_Error = "Std. Err.",
    z = "z",
    P_value = "P>|z|",
    CI_Lower = "95% CI Lower",
    CI_Upper = "95% CI Upper"
  ) %>%
  fmt_number(
    columns = c(Coef, Std_Error, z, P_value, CI_Lower, CI_Upper),
    decimals = 4
  ) %>%
  tab_options(
    table.font.size = 13,
    heading.title.font.size = 16,
    heading.subtitle.font.size = 13
  )

pairwise_corr_gt

gtsave(
  pairwise_corr_gt,
  filename = "pairwise_dcc_correlations_no_sp500.png"
)
```

## 13. Create Daily Dynamic Correlation Dataset

This section focuses on the correlations between Shanghai and the other Asian markets.

```{r}
dcc_daily <- data.frame(
  Date = daily_returns$Date,
  corr_SH_Hang_Seng = dcc_cor_no_sp500[1, 2, ],
  corr_SH_Nikkei = dcc_cor_no_sp500[1, 3, ],
  corr_SH_KOSPI = dcc_cor_no_sp500[1, 4, ],
  corr_SH_STI = dcc_cor_no_sp500[1, 5, ]
)

head(dcc_daily)
summary(dcc_daily)
```

## 14. Average Shanghai-Market Dynamic Correlations

```{r}
avg_shanghai_cor <- data.frame(
  Market_Pair = c(
    "Shanghai-Hang Seng",
    "Shanghai-Nikkei",
    "Shanghai-KOSPI",
    "Shanghai-STI"
  ),
  Average_DCC_Correlation = c(
    mean(dcc_daily$corr_SH_Hang_Seng, na.rm = TRUE),
    mean(dcc_daily$corr_SH_Nikkei, na.rm = TRUE),
    mean(dcc_daily$corr_SH_KOSPI, na.rm = TRUE),
    mean(dcc_daily$corr_SH_STI, na.rm = TRUE)
  )
)

avg_shanghai_cor
```

## 15. Export Daily Dynamic Correlations

```{r}
write.csv(dcc_daily, "dcc_dynamic_correlations_daily_no_sp500.csv", row.names = FALSE)
```

## 16. Plot All Shanghai Dynamic Correlations

```{r}
dcc_long <- dcc_daily %>%
  pivot_longer(
    cols = starts_with("corr_"),
    names_to = "Market_Pair",
    values_to = "Correlation"
  )

ggplot(dcc_long, aes(x = Date, y = Correlation, color = Market_Pair)) +
  geom_line(linewidth = 0.5) +
  labs(
    title = "Dynamic Conditional Correlations with Shanghai Market",
    subtitle = "Five Asian markets, excluding S&P 500",
    x = "Date",
    y = "Dynamic Correlation",
    color = "Market Pair"
  ) +
  theme_minimal()
```

## 17. Plot Individual Shanghai Dynamic Correlations

```{r}
# Shanghai-Hang Seng
plot_sh_hs <- ggplot(dcc_daily, aes(x = Date, y = corr_SH_Hang_Seng)) +
  geom_line(linewidth = 0.5) +
  labs(
    title = "Dynamic Conditional Correlation: Shanghai and Hang Seng",
    x = "Date",
    y = "Dynamic Correlation"
  ) +
  theme_minimal()

plot_sh_hs

# Shanghai-Nikkei
plot_sh_nikkei <- ggplot(dcc_daily, aes(x = Date, y = corr_SH_Nikkei)) +
  geom_line(linewidth = 0.5) +
  labs(
    title = "Dynamic Conditional Correlation: Shanghai and Nikkei 225",
    x = "Date",
    y = "Dynamic Correlation"
  ) +
  theme_minimal()

plot_sh_nikkei

# Shanghai-KOSPI
plot_sh_kospi <- ggplot(dcc_daily, aes(x = Date, y = corr_SH_KOSPI)) +
  geom_line(linewidth = 0.5) +
  labs(
    title = "Dynamic Conditional Correlation: Shanghai and KOSPI",
    x = "Date",
    y = "Dynamic Correlation"
  ) +
  theme_minimal()

plot_sh_kospi

# Shanghai-STI
plot_sh_sti <- ggplot(dcc_daily, aes(x = Date, y = corr_SH_STI)) +
  geom_line(linewidth = 0.5) +
  labs(
    title = "Dynamic Conditional Correlation: Shanghai and Singapore STI",
    x = "Date",
    y = "Dynamic Correlation"
  ) +
  theme_minimal()

plot_sh_sti
```

## 18. Save Individual Plots

```{r}
ggsave("dcc_shanghai_hang_seng_no_sp500.png", plot_sh_hs, width = 8, height = 5, dpi = 300)
ggsave("dcc_shanghai_nikkei_no_sp500.png", plot_sh_nikkei, width = 8, height = 5, dpi = 300)
ggsave("dcc_shanghai_kospi_no_sp500.png", plot_sh_kospi, width = 8, height = 5, dpi = 300)
ggsave("dcc_shanghai_sti_no_sp500.png", plot_sh_sti, width = 8, height = 5, dpi = 300)
```

## 19. Suggested Interpretation Notes

The DCC-GARCH results can be interpreted together with the VAR and Granger causality results.

If the average dynamic correlations between Shanghai and the other Asian markets are relatively low, this may support the argument that China's stock market linkages with other Asian markets are weaker than expected. If the correlations increase during crisis periods, such as the Global Financial Crisis or COVID-19 period, this may suggest stronger co-movement during market stress.
