---
title: "DCC - GARCH"
format: docx
editor: visual
---

## 1. Load Packages

```{r}
packages <- c("readr", "dplyr", "lubridate", "rugarch", "rmgarch", 
              "xts", "zoo", "ggplot2", "tidyr", "gt")

# Load the packages listed above.
lapply(packages, library, character.only = TRUE)
```

## 2. Import Daily Index Price Data

The extended model uses the same common six-market trading-date sample as the baseline model. This keeps the sample period and observation count identical across the two DCC-GARCH specifications.

The repository includes a frozen local dataset ending on 2023-08-31. Rendering this document does not download or update market data.

```{r}
data_candidates <- c(
  "../../dataset/outputs/daily_prices_all_markets.csv",
  "dataset/outputs/daily_prices_all_markets.csv",
  "daily_prices_all_markets.csv"
)
data_path <- data_candidates[file.exists(data_candidates)][1]

if (is.na(data_path)) {
  stop("The frozen daily_prices_all_markets.csv included with the project was not found.")
}

daily_prices <- readr::read_csv(data_path)

head(daily_prices)
str(daily_prices)

```

## 3. Clean Date and Restrict Sample Period

```{r}
daily_prices <- daily_prices %>%
  mutate(Date = as.Date(Date)) %>%
  arrange(Date) %>%
  filter(Date >= as.Date("2003-01-01"),
         Date <= as.Date("2023-08-31"))

head(daily_prices)
tail(daily_prices)
summary(daily_prices)
colSums(is.na(daily_prices))
sum(duplicated(daily_prices$Date))
nrow(daily_prices)
```

## 4. Calculate Daily Log Returns

```{r}
daily_returns <- daily_prices %>%
  mutate(
    r_STI = (log(STI) - log(lag(STI))) * 100,
    r_Hang_Seng = (log(Hang_Seng) - log(lag(Hang_Seng))) * 100,
    r_KOSPI = (log(KOSPI) - log(lag(KOSPI))) * 100,
    r_Nikkei_225 = (log(Nikkei_225) - log(lag(Nikkei_225))) * 100,
    r_SP500 = (log(SP500) - log(lag(SP500))) * 100,
    r_Shanghai = (log(Shanghai_Composite) - log(lag(Shanghai_Composite))) * 100
  ) %>%
  select(
    Date,
    r_Shanghai,
    r_Hang_Seng,
    r_Nikkei_225,
    r_KOSPI,
    r_STI,
    r_SP500
  ) %>%
  na.omit()

nrow(daily_returns)
colSums(is.na(daily_returns))
```

## 4.1 Daily Data Audit and Descriptive Statistics

The audit table records how the common daily price sample becomes the return sample used in the extended DCC-GARCH estimation. The descriptive table includes the five Asian return series and the S&P 500 return.

```{r}
daily_data_audit <- data.frame(
  Stage = c("Common six-market daily prices", "Extended daily returns"),
  Observations = c(nrow(daily_prices), nrow(daily_returns)),
  Start_Date = c(as.character(min(daily_prices$Date)), as.character(min(daily_returns$Date))),
  End_Date = c(as.character(max(daily_prices$Date)), as.character(max(daily_returns$Date))),
  Missing_Values = c(sum(is.na(daily_prices)), sum(is.na(daily_returns))),
  Duplicate_Dates = c(sum(duplicated(daily_prices$Date)), sum(duplicated(daily_returns$Date)))
)

daily_data_audit

return_variables <- setdiff(names(daily_returns), "Date")

daily_descriptive_statistics <- do.call(rbind, lapply(return_variables, function(variable) {
  x <- daily_returns[[variable]]
  n <- length(x)
  x_mean <- mean(x)
  x_sd <- sd(x)
  skewness <- mean((x - x_mean)^3) / x_sd^3
  excess_kurtosis <- mean((x - x_mean)^4) / x_sd^4 - 3
  jb_statistic <- n / 6 * (skewness^2 + excess_kurtosis^2 / 4)

  data.frame(
    Variable = variable,
    N = n,
    Mean = x_mean,
    Std_Dev = x_sd,
    Minimum = min(x),
    Maximum = max(x),
    Skewness = skewness,
    Excess_Kurtosis = excess_kurtosis,
    JB_Statistic = jb_statistic,
    JB_p_value = pchisq(jb_statistic, df = 2, lower.tail = FALSE)
  )
}))

daily_descriptive_statistics
```

## 5. Export Cleaned Daily Returns

```{r}
write.csv(daily_returns, "daily_returns_for_dcc.csv", row.names = FALSE)
```

## 6. Estimate DCC-GARCH Model

```{r}
# Keep only return variables for DCC-GARCH
dcc_data_with_sp500 <- daily_returns %>%
  select(
    r_Shanghai,
    r_Hang_Seng,
    r_Nikkei_225,
    r_KOSPI,
    r_STI,
    r_SP500
  )

# Check data
head(dcc_data_with_sp500)
summary(dcc_data_with_sp500)
```

## 7. Set up DCC-GARCH Specification

```{r}
# Univariate GARCH(1,1) specification for each market
uspec_with_sp500 <- ugarchspec(
  mean.model = list(armaOrder = c(0, 0), include.mean = TRUE),
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  distribution.model = "norm"
)

# Apply the same GARCH specification to all return series
multispec_model_with_sp500 <- multispec(replicate(ncol(dcc_data_with_sp500), uspec_with_sp500))

# DCC-GARCH(1,1) specification
dcc_spec_with_sp500 <- dccspec(
  uspec = multispec_model_with_sp500,
  dccOrder = c(1, 1),
  distribution = "mvnorm"
)
```

## 8. Fit DCC-GARCH Model

```{r}
dcc_fit_with_sp500 <- dccfit(
  dcc_spec_with_sp500,
  data = dcc_data_with_sp500
)

# Create a clean parameter table
dcc_param_table_with_sp500 <- as.data.frame(dcc_fit_with_sp500@mfit$matcoef)

# Add parameter names
dcc_param_table_with_sp500$Parameter <- rownames(dcc_param_table_with_sp500)

# Rename columns manually
colnames(dcc_param_table_with_sp500) <- c(
  "Estimate",
  "Std_Error",
  "t_value",
  "p_value",
  "Parameter"
)

# Reorder columns and add confidence intervals
dcc_param_table_with_sp500 <- dcc_param_table_with_sp500 %>%
  select(Parameter, Estimate, Std_Error, t_value, p_value) %>%
  mutate(
    CI_Lower = Estimate - 1.96 * Std_Error,
    CI_Upper = Estimate + 1.96 * Std_Error
  )

# Display as a clean table
dcc_param_gt_with_sp500 <- dcc_param_table_with_sp500 %>%
  gt::gt() %>%
  gt::tab_header(
    title = "DCC-GARCH Parameter Estimates"
  ) %>%
  gt::cols_label(
    Parameter = "Parameter",
    Estimate = "Estimate",
    Std_Error = "Std. Error",
    t_value = "t value",
    p_value = "p-value",
    CI_Lower = "95% CI Lower",
    CI_Upper = "95% CI Upper"
  ) %>%
  gt::fmt_number(
    columns = c(Estimate, Std_Error, t_value, p_value, CI_Lower, CI_Upper),
    decimals = 6
  )
dcc_param_gt_with_sp500

gt::gtsave(
  dcc_param_gt_with_sp500,
  filename = "dcc_garch_parameter_estimates.png"
)
```

## 9. Extract Daily Dynamic Correlations

```{r}
# Extract dynamic correlation array
dcc_cor_with_sp500 <- rcor(dcc_fit_with_sp500)

avg_dcc_cor_matrix_with_sp500 <- apply(dcc_cor_with_sp500, c(1, 2), mean, na.rm = TRUE)

colnames(avg_dcc_cor_matrix_with_sp500) <- colnames(dcc_data_with_sp500)
rownames(avg_dcc_cor_matrix_with_sp500) <- colnames(dcc_data_with_sp500)

knitr::kable(
  avg_dcc_cor_matrix_with_sp500,
  digits = 4,
  caption = "Average Dynamic Conditional Correlation Matrix"
)
# Check dimensions
dim(dcc_cor_with_sp500)
```

```{r}
## Stata-style Pairwise Dynamic Correlation Table
make_corr_row <- function(x, pair_name) {
  x <- na.omit(x)
  coef <- mean(x)
  se <- sd(x) / sqrt(length(x))
  z_value <- coef / se
  p_value <- 2 * (1 - pnorm(abs(z_value)))
  ci_lower <- coef - 1.96 * se
  ci_upper <- coef + 1.96 * se
  
  data.frame(
    Pair = pair_name,
    Coef = coef,
    Std_Error = se,
    z = z_value,
    P_value = p_value,
    CI_Lower = ci_lower,
    CI_Upper = ci_upper
  )
}

pairwise_corr_table <- rbind(
  make_corr_row(dcc_cor_with_sp500[1, 2, ], "corr(r_SH, r_Hang_Seng)"),
  make_corr_row(dcc_cor_with_sp500[1, 3, ], "corr(r_SH, r_Nikkei)"),
  make_corr_row(dcc_cor_with_sp500[1, 4, ], "corr(r_SH, r_KOSPI)"),
  make_corr_row(dcc_cor_with_sp500[1, 5, ], "corr(r_SH, r_STI)"),
  make_corr_row(dcc_cor_with_sp500[1, 6, ], "corr(r_SH, r_SP500)"),
  make_corr_row(dcc_cor_with_sp500[2, 3, ], "corr(r_Hang_Seng, r_Nikkei)"),
  make_corr_row(dcc_cor_with_sp500[2, 4, ], "corr(r_Hang_Seng, r_KOSPI)"),
  make_corr_row(dcc_cor_with_sp500[2, 5, ], "corr(r_Hang_Seng, r_STI)"),
  make_corr_row(dcc_cor_with_sp500[2, 6, ], "corr(r_Hang_Seng, r_SP500)"),
  make_corr_row(dcc_cor_with_sp500[3, 4, ], "corr(r_Nikkei, r_KOSPI)"),
  make_corr_row(dcc_cor_with_sp500[3, 5, ], "corr(r_Nikkei, r_STI)"),
  make_corr_row(dcc_cor_with_sp500[3, 6, ], "corr(r_Nikkei, r_SP500)"),
  make_corr_row(dcc_cor_with_sp500[4, 5, ], "corr(r_KOSPI, r_STI)"),
  make_corr_row(dcc_cor_with_sp500[4, 6, ], "corr(r_KOSPI, r_SP500)"),
  make_corr_row(dcc_cor_with_sp500[5, 6, ], "corr(r_STI, r_SP500)")
)

pairwise_corr_table %>%
  gt() %>%
  tab_header(
    title = "Pairwise Dynamic Conditional Correlations",
    subtitle = "DCC-GARCH estimated correlations"
  ) %>%
  cols_label(
    Pair = "Pair",
    Coef = "Coef.",
    Std_Error = "Std. Err.",
    z = "z",
    P_value = "P>|z|",
    CI_Lower = "95% CI Lower",
    CI_Upper = "95% CI Upper"
  ) %>%
  fmt_number(
    columns = c(Coef, Std_Error, z, P_value, CI_Lower, CI_Upper),
    decimals = 4
  ) %>%
  tab_options(
    table.font.size = 13,
    heading.title.font.size = 16,
    heading.subtitle.font.size = 13
  )
```

## . Create Daily Dynamic Correlation Dataset

```{r}
# Extract correlations between Shanghai and other markets
corr_SH_Hang_Seng <- dcc_cor_with_sp500[1, 2, ]
corr_SH_Nikkei <- dcc_cor_with_sp500[1, 3, ]
corr_SH_KOSPI <- dcc_cor_with_sp500[1, 4, ]
corr_SH_STI <- dcc_cor_with_sp500[1, 5, ]
corr_SH_SP500 <- dcc_cor_with_sp500[1, 6, ]

# Create daily DCC correlation dataset
dcc_daily <- data.frame(
  Date = daily_returns$Date,
  corr_SH_Hang_Seng = corr_SH_Hang_Seng,
  corr_SH_Nikkei = corr_SH_Nikkei,
  corr_SH_KOSPI = corr_SH_KOSPI,
  corr_SH_STI = corr_SH_STI,
  corr_SH_SP500 = corr_SH_SP500
)

head(dcc_daily)
summary(dcc_daily)
```

```{r}
## 11. Average Dynamic Conditional Correlations

# Calculate average dynamic correlations between Shanghai and other markets
avg_shanghai_cor <- data.frame(
  Market_Pair = c(
    "Shanghai-Hang Seng",
    "Shanghai-Nikkei",
    "Shanghai-KOSPI",
    "Shanghai-STI",
    "Shanghai-SP500"
  ),
  Average_DCC_Correlation = c(
    mean(dcc_daily$corr_SH_Hang_Seng, na.rm = TRUE),
    mean(dcc_daily$corr_SH_Nikkei, na.rm = TRUE),
    mean(dcc_daily$corr_SH_KOSPI, na.rm = TRUE),
    mean(dcc_daily$corr_SH_STI, na.rm = TRUE),
    mean(dcc_daily$corr_SH_SP500, na.rm = TRUE)
  )
)

avg_shanghai_cor
```

```{r}
## 11. Average Dynamic Conditional Correlations

# Calculate the average dynamic conditional correlation matrix
avg_dcc_cor_matrix_with_sp500 <- apply(dcc_cor_with_sp500, c(1, 2), mean, na.rm = TRUE)

# Add market names
colnames(avg_dcc_cor_matrix_with_sp500) <- colnames(dcc_data_with_sp500)
rownames(avg_dcc_cor_matrix_with_sp500) <- colnames(dcc_data_with_sp500)

# Display the full average DCC correlation matrix
knitr::kable(
  avg_dcc_cor_matrix_with_sp500,
  digits = 4,
  caption = "Average Dynamic Conditional Correlation Matrix"
)
```

## 11. Export Daily Dynamic Correlations

```{r}
write.csv(dcc_daily, "dcc_dynamic_correlations_daily.csv", row.names = FALSE)
```

## 12. Plot Daily Dynamic Correlations

```{r}
library(ggplot2)
library(tidyr)

dcc_long <- dcc_daily %>%
  pivot_longer(
    cols = starts_with("corr_"),
    names_to = "Market_Pair",
    values_to = "Correlation"
  )

ggplot(dcc_long, aes(x = Date, y = Correlation, color = Market_Pair)) +
  geom_line(linewidth = 0.5) +
  labs(
    title = "Dynamic Conditional Correlations with Shanghai Market",
    x = "Date",
    y = "Dynamic Correlation",
    color = "Market Pair"
  ) +
  theme_minimal()
```

```{r}
## 12.1 Plot Shanghai-Hang Seng Dynamic Correlation

ggplot(dcc_daily, aes(x = Date, y = corr_SH_Hang_Seng)) +
  geom_line(linewidth = 0.5) +
  labs(
    title = "Dynamic Conditional Correlation: Shanghai and Hang Seng",
    x = "Date",
    y = "Dynamic Correlation"
  ) +
  theme_minimal()
```

```{r}
# Shanghai-Hang Seng
plot_sh_hs <- ggplot(dcc_daily, aes(x = Date, y = corr_SH_Hang_Seng)) +
  geom_line(linewidth = 0.5) +
  labs(
    title = "Dynamic Conditional Correlation: Shanghai and Hang Seng",
    x = "Date",
    y = "Dynamic Correlation"
  ) +
  theme_minimal()

plot_sh_hs

# Shanghai-Nikkei
plot_sh_nikkei <- ggplot(dcc_daily, aes(x = Date, y = corr_SH_Nikkei)) +
  geom_line(linewidth = 0.5) +
  labs(
    title = "Dynamic Conditional Correlation: Shanghai and Nikkei 225",
    x = "Date",
    y = "Dynamic Correlation"
  ) +
  theme_minimal()

plot_sh_nikkei

# Shanghai-KOSPI
plot_sh_kospi <- ggplot(dcc_daily, aes(x = Date, y = corr_SH_KOSPI)) +
  geom_line(linewidth = 0.5) +
  labs(
    title = "Dynamic Conditional Correlation: Shanghai and KOSPI",
    x = "Date",
    y = "Dynamic Correlation"
  ) +
  theme_minimal()

plot_sh_kospi

# Shanghai-STI
plot_sh_sti <- ggplot(dcc_daily, aes(x = Date, y = corr_SH_STI)) +
  geom_line(linewidth = 0.5) +
  labs(
    title = "Dynamic Conditional Correlation: Shanghai and STI",
    x = "Date",
    y = "Dynamic Correlation"
  ) +
  theme_minimal()

plot_sh_sti

# Shanghai-S&P 500
plot_sh_sp500 <- ggplot(dcc_daily, aes(x = Date, y = corr_SH_SP500)) +
  geom_line(linewidth = 0.5) +
  labs(
    title = "Dynamic Conditional Correlation: Shanghai and S&P 500",
    x = "Date",
    y = "Dynamic Correlation"
  ) +
  theme_minimal()

plot_sh_sp500
```

```{r}
ggplot(dcc_daily, aes(x = Date, y = corr_SH_Nikkei)) +
  geom_line(linewidth = 0.5) +
  labs(
    title = "Dynamic Conditional Correlation: Shanghai and Nikkei 225",
    x = "Date",
    y = "Dynamic Correlation"
  ) +
  theme_minimal()
```
